cardinalR: Generating interesting high-dimensional data structures

### 2025-04-26 paper-cardinalR.Rmd
Added Figure title

```{r, label = "fig-nldr-layouts", fig.cap="Six Drs"}
nldr1 + nldr2 + nldr3 +
  nldr4 + nldr5 + nldr6 +
  plot_layout(ncol = 3)
```

>>>>

```{r, label = "fig-nldr-layouts", fig.cap="Six different dimension reduction representations of the `mobiusgau` data using default hyperparameter settings: (a) tSNE, (b) UMAP, (c) PAHTE, (d) TriMAP, (e) PaCMAP, and (f) PCA."}
nldr1 + nldr2 + nldr3 +
  nldr4 + nldr5 + nldr6 +
  plot_layout(ncol = 3)
```
